Monster or Lambda?  A likelihood analysis

### 2025-02-07 inst/monster_vs_lambda.Rmd
consistentify "time to process" information
include theoretical result

---
title: "Monster or Lambda?  A likelihood analysis"
subtitle: "Takes about an hour to run without cache"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

@@

This is equal to $(\alpha+\delta)\log\lambda +(\alpha+\gamma)\log
A+(\beta+\delta)\log B -(\alpha+\beta)\log(\lambda A+B)
-(\gamma+\delta)\log(A+\lambda B)$ and even after simplifying [we may
assume $B=1-A$] the result of maximizing $\mathcal{S}$ with respect to
$A$ and $\lambda$ does not appear to have a simple analytical
solution; we must proceed numerically.  To do so, we need to define a
slight generalization of `home_away3()`:

>>>>

---
title: "Monster or Lambda?  A likelihood analysis"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

<font size="1"> (takes about an hour to run without cache)
</font>

@@

This is equal to $(\alpha+\delta)\log\lambda +(\alpha+\gamma)\log
A+(\beta+\delta)\log B -(\alpha+\beta)\log(\lambda A+B)
-(\gamma+\delta)\log(A+\lambda B)$ and even after simplifying [we may
assume $B=1-A$] the result of maximizing $\mathcal{S}$ with respect to
$A$ and $\lambda$ gives the following result:

$$
\hat{A} = \frac{\sqrt{\alpha\gamma}}{\sqrt{\alpha\gamma} + \sqrt{\beta\delta}}
$$

$$
\hat{\lambda} = \sqrt{\frac{\alpha\delta}{\beta\gamma}}
$$
